Adding selection to \stdpopsim: oh how the tables have turned

### 2025-01-10 analysis2_manuscript.tex
Update analysis2_manuscript.tex

    A challenge when comparing quantitative DFE estimates among tools and with simulations is differing conventions of factors of two in terms of how the selection coefficient ($s$) is delimited.
    The simulator SLiM and the inference tool \grapes define the selection coefficient $s$ such that a homozygote has fitness $1+s$.
    On the other hand, \dadicli and \polydfe define the selection coefficient such that a homozygote has fitness $1+ 2s$. %https://academic.oup.com/genetics/article/207/3/1103/5930676
    Moreover, all three inference tools directly infer the distribution of the selection coefficient scaled by an inferred ancestral effective population size $N_e$, but they assume different scaling.
    \dadicli infers the distribution of $2 N_e s$ while \polydfe and \grapes infer the distribution of $4 N_e s$. %https://academic.oup.com/genetics/article/207/3/1103/5930676, https://academic.oup.com/genetics/article/216/2/559/6066183
    For comparison, here we have normalized all inference results to the convention of SLiM.

>>>>

    A challenge when comparing quantitative DFE estimates among tools and with simulations is differing conventions of factors of two in terms of how the selection coefficient ($s$) is defined.
    The simulator SLiM and the inference tool \grapes define the selection coefficient $s$ such that a homozygote has fitness $1+s$.
    On the other hand, \dadicli and \polydfe define the selection coefficient such that a homozygote has fitness $1+ 2s$. %https://academic.oup.com/genetics/article/207/3/1103/5930676
    Moreover, all three inference tools directly infer the distribution of the selection coefficient scaled by an inferred ancestral effective population size $N_e$, but they assume different scaling.
    \dadicli infers the distribution of $2 N_e s$ while \polydfe and \grapes infer the distribution of $4 N_e s$. %https://academic.oup.com/genetics/article/207/3/1103/5930676, https://academic.oup.com/genetics/article/216/2/559/6066183
    For comparison, here we have normalized all inference results to the convention of SLiM.
